% Last update: 2004-01-28
\documentclass{article}
\begin{document}

\parindent=0pt
\addtolength{\parskip}{3pt}
\addtolength{\textwidth}{10em}
\addtolength{\textheight}{12em}
\def\tc{\mathaccent"7017}
\textwidth=400pt
\section*{Publications of Tatyana Shaposhnikova}

\pagestyle{myheadings}\thispagestyle{empty}
\markboth{Publications of Tatyana Shaposhnikova}
            {Publications of Tatyana Shaposhnikova}
\subsection*{Books}

\begin{enumerate}
\item Maz'ya V., Shaposhnikova T. {\it Theory of Multipliers in
Spaces of Differentiable Functions}, Pitman, 1985 (Russian
version: Leningrad University Press, 1986).

\item Shaposhnikova T., Polyshchuk E. {\it Jacques Hadamard}, Nauka,
Leningrad, 1990.

\item Maz'ya V., Shaposhnikova T. , {\it Jacques Hadamard, a
Universal Mathematician}, American Mathematical Society and
London Mathematical Society, 1998.

\item Maz'ya, V., Shaposhnikova, T., 
{\it Jacques Hadamard, un Math\'ematicien Universel}. EDP Sciences, Paris, 2005 
(revised and extended translation from English).

\item 
{\it Sharp Real-Part Theorems. A Unified Approach} by G. Kresin and V. Maz'ya. Translated from Russian and edited by T. Shaposhnikova, Lecture Notes in Mathematics, N. 1903, Springer, 2007.

\item Maz'ya V., Shaposhnikova T., {\it Jacques Hadamard, Legend of  Mathematics}. MCNMO Publishers, Moscow, 2008 (revised,  extended, and  authorized translation from English to Russian).

\item Maz'ya V., Shaposhnikova T., {\it Theory of Sobolev Multipliers with Applications to Differential and Integral Operators}, Grundlehren der Mathematischen Wissenschaften, vol. 337, Springer, 2009.


\item
{\it Boundary Integral Equations on Contours with Peaks} by V. Maz'ya and A. Soloviev. Translated from Russian and edited by T. Shaposhnikova, Operator Theory Advances and Applications, Vol.196, Birkh\"auser,  2010.

\end{enumerate}


\subsection*{Papers}

\begin{enumerate}
\item Shaposhnikova T., {\it Some a priori estimates for variational
methods}, Vestnik
Leningrad Univ. {\bf 19} (1971), 64--69.

\item Shaposhnikova T., {\it Asymptotic estimates for convergence of
the Ritz method in
eigenvalue problems}, Izvestia Vys. Uch. Zav. Math. {\bf 6} (1972),
86--91.

\item Shaposhnikova T., {\it A priori estimates for the Ritz method
in eigenvalue problems
to degernate elliptic high order operators}, Izvestia Vys. Uch. Zav.
Math. {\bf 5} (1973), 99--108.

\item Shaposhnikova T., {\it Asymptotic error estimates for the Ritz
method in eigenvalue
problems to a degenerate elliptic operator}, Diff. Uravnen. {\bf 9}:4
(1973), 709--716.

\item Shaposhnikova T., {\it On a modification of the method of
intermediate problems},
Izvestia Vys. Uch. Zav. Math. {\bf 3}:3 (1974), 89--92.

\item Shaposhnikova T., {\it Net approximation for solutions of
degenerate equations in
weighted norms}, Diff. Uravnenia {\bf 11}:11 (1975), 2261--2268.

\item Shaposhnikova T., {\it A priori estimates for some variational
methods in Sobolev
spaces}, Trudy Seminara "Variational difference methods in Mathematics
Phy\-sics", Novosibirsk, 1976, 182-194.

\item Shaposhnikova T., {\it A priori estimates for variational
methods in Banach spaces},
J. Vychisl. Math. and Math. Phys. {\bf 17}:5 (1977), 1144--1152.

\item Shaposhnikova T., {\it Net approximation of solutions of
degenerate ordinary
differential equ\-ations of the second order}, Matem. Zametki {\bf
24}:1 (1978), 95--101.

\item Maz'ya V.G., Shaposhnikova T., {\it On multipliers in spaces of
functions with fractional
derivatives}, Dokl. Acad. Nauk USSR {\bf 244}:5 (1979), 1065--1067.

\item Maz'ya V.G., Shaposhnikova T., {\it Traces and extensions of
multipliers in the space
$W_p$}, Uspehi Math. Nauk {\bf 34}:2 (1979), 205--206.

\item Maz'ya V.G., Shaposhnikova T., {\it On multipliers in Sobolev
spaces}, Vestnik Leningrad Univ. {\bf 7}
(1979), 33--40.

\item Maz'ya V.G., Shaposhnikova T., {\it Theory of multipliers in
spaces of differentiable functions
and its applications}, Uspehi Math. Nauk {\bf 34}:4 (1979), 144--145.


\item Maz'ya V.G., Shaposhnikova T., {\it Coercive estimates for
solutions of elliptic equations in
spaces of multipliers}, Vestnik Leningrad Univ. {\bf 1} (1980),
41--47.

\item Maz'ya V.G., Shaposhnikova T., {\it On conditions to the
boundary in $L_p$-theory of elliptic
boundary value problems}, Dokl. Acad. Nauk {\bf 251}:5 (1980),
1055-1059.

\item Maz'ya V.G., Shaposhnikova T., {\it Multipliers in spaces of
differentiable functions}, Trudy
Seminara S.L. Soboleva {\bf 1} (1979), 37--90.

\item Shaposhnikova T., {\it On conditions on the boundary in
$L_p$-theory of elliptic
boundary value problems}, Uspehi Math. Nauk {\bf 35}:4 (1980), 774.

\item Shaposhnikova T., {\it Equivalent norms in spaces of functions
with fractional or
functional smoothness}, Sibir. Math. J. {\bf 21}:3 (1980), 184--196.

\item Maz'ya V.G., Shaposhnikova T., {\it Multipliers in pairs of
potential spaces}, Math. Nachr. {\bf 99}
(1980), 363--379.

\item Maz'ya V.G., Shaposhnikova T., {\it Multipliers in Sobolev
spaces in a domain}, Math. Nachr. {\bf 99}
(1980), 165--183.

\item Maz'ya V.G., Shaposhnikova T., {\it Multipliers in pairs of
spaces of differentiable functions},
Trudy Moscow Math. Soc. {\bf 43} (1981), 37--80.

\item Maz'ya V.G., Shaposhnikova T., {\it On regularity of the
boundary in $L_p$-theory of elliptic
boundary value problems}, Trudy Seminara S.L. Sobolev, Novosibirsk
{\bf 1}
(1981), 57-102.

\item Maz'ya V.G., Shaposhnikova T., {\it On sufficient conditions to
belong to classes of
multipliers}, Math. Nachr. {\bf 100} (1981), 151--162.

\item Maz'ya V.G., Shaposhnikova T., {\it Multipliers in spaces
$W_p^m$ and their applications},
Vestnik Leningrad Univ. {\bf 1}(1981), 42--47.

\item Shaposhnikova T., {\it Multipliers in pairs of spaces of
differentiable functions},
Boundary Value Problems in Math. Phys., Donetsk (1981), 142-145.

\item Maz'ya V.G., Shaposhnikova T., {\it The change of variables as
an operator in a pair of Sobolev
spaces}, Vestnik Leningrad Univ. {\bf 1} (1982), 43--48.

\item Maz'ya V.G., Shaposhnikova T., {\it Multipliers in spaces of
differentiable functions}, Uspehi
Math. Nauk {\bf 38}:3 (1983), 23--86.

\item Shaposhnikova T., {\it On continuity of differential operators
in pairs of Sobolev
spaces}, VIII School on Operator Theory in functional Spaces, Riga
(1983), 122--123.

\item Shaposhnikova T., {\it Positive homogeneous multipliers in
Riesz and Bessel
potential spaces}, Preprint P-Math-07185: Akad. Wissenschaften DDR,
Inst. Math. Berlin, 1985, 1-16.

\item Shaposhnikova T., {\it On the spectrum of multipliers in Bessel
potential spaces},
Casopis pro pestovani mat. {\bf 110} (1985), 197--206.

\item Shaposhnikova T., {\it On continuity of differential operators
in Sobolev spaces},
Uspehi Math. Nauk {\bf 40}:5 (1985), 189.

\item Shaposhnikova T., {\it Bounded solutions of elliptic equations
as multipliers in
spaces of differentiable functions}, Zapiski Nauchn. Semin. LOMI {\bf
149} (1986), 165--176.

\item Shaposhnikova T., {\it Multiplicative properties of solutions of
elliptic
equations}, Uspehi Math. Nauk {\bf 41}:4 (1986), 209.

\item Shaposhnikova T., {\it Implicit mapping theorem for multipliers
in Bessel potential
spaces}, Izvestia Azerb. SSR {\bf 1} (1987),14--18.

\item Shaposhnikova T., {\it On solvability of quasilinear elliptic
equations in spaces
of multipliers}, Izvestia Vis. Uch. Zav. Math. {\bf 8} (1987), 74--81.

\item Shaposhnikova T., {\it Multipliers in $L_p$-theory of elliptic
boundary value
problems}, Nonlinear problems in Math. Phys.: VI Republic Conference,
Donetsk, 1987, 160.

\item Shaposhnikova T. {\it On the superposition operator in classes
of multipliers in
Sobolev spaces}, Seminar Analysis: Inst. Math. Berlin (1987),
181--190.

\item Shaposhnikova T., {\it On nonlinear differential operators in
spaces of
multipliers}, Uspehi Math. Nauk {\bf 42}:4 (1987), 158.

\item Shaposhnikova T., {\it On coercivity in $L_p$ of the Neumann
problem in a domain
with nonsmooth boundary}, Uspehi Math. Nauk {\bf 43}:4 (1988), 181.

\item Shaposhnikova T., {\it Implicit mapping theorem for multipliers
in spaces $W_p^l$},
Functional and Numerical Methods in Math. Phys.: Kiev, 1988, 241--245.

\item Shaposhnikova T., {\it Multipliers in Bessel potential spaces
as traces of
multipliers in weighted classes}, Trudy Math. Inst. Georgian Acad.
Nauk
{\bf 88} (1989), 59--63.

\item Shaposhnikova T., {\it Traces of multipliers in Bessel
potential spaces}, Math.
Zametki {\bf 46}:3 (1989), 100--109.

\item Shaposhnikova T., {\it Applications of multipliers in Sobolev
spaces to
$L_p$-coercivity of the Neumann problem}, Dokl. Acad. Nauk USSR,
{\bf 305}:4 (1989), 786--789.

\item Shaposhnikova T., {\it Applications of multipliers to the
problem of coercivity of
the Neumann problem in $W^\ell_p$}, Problemy Math. Anal. {\bf 11}
(1990), 237--248.

\item Shaposhnikova T., {\it On continuity of singular integral
operators in Sobolev spaces},
Mathematica Scandinavica, {\bf 76} (1995), 85-97.

\item Shaposhnikova T., {\it On continuity of singular integral
operators in Sobolev spaces}, IABEM Symposium on boundary integral
methods for nonlinear problems, Kluwer Academic Publishers, 1997,
191-195.

\item Eidus D., Khvoles A., Kresin G., Merzbach E., Pr\"osdorf S.,
Shaposhnikova T., Sobolevskii P., Solomiak M., {\it
Mathematical work of Vladimir Maz'ya}, Functional Differential
Equations {\bf 4}:1 (1997), 3-11.

\item  Shaposhnikova T., {\it Sobolev multipliers in a non-smooth
$L_p$ elliptic theory}, Analysis,
Numerics and Applications of Differential and Integral Equations,
Pitman Research Notes in Mathematical Series, {\bf 379}, 1998,
205-208.


\item Maz'ya V., Shaposhnikova, T. {\it On pointwise interpolation
inequalities for derivatives}, Mathematica Bohemica, {\bf
124}, 1999, 131-148.

\item Shaposhnikova T., {\it Multipliers of differentiable functions
and
their traces}, Proceedings of the Coinference on Honour of
Vladimir Maz'ya ``Functional Analysis, Partial Differential Equations
and
Applications'', v.1, Birkh\"auser, Basel, 1999, 155-169.

\item Shaposhnikova T., {\it Sobolev multipliers in the theory of
integral
convolution operators}, Mathematical Aspects of Boundary
Integral Methods, Chapman and Hall, London, 1999, 285-295.

\item Maz'ya V., Shaposhnikova, T. {\it Traces and extensions of
multipliers in pairs of Sobolev spaces},
Operator Theory, Advances and Applications. Vol. 113: S.A. Vinogradov
- In
Memoriam, Birkh\"auser, 2000, 221-237.

\item Maz'ya V., Shaposhnikova, T., {\it Pointwise interpolation
inequalities for Riesz and Bessel potentials}, Analytical and
Computational Methods in Scattering and Applied Mathematics, Chapman
and
Hall, London, 2000, 217-229.

\item Shaposhnikova, T. {\it Sobolev multipliers in the $L_p$ theory
of
boundary integral equations of elasticity
    on  non-smooth surfaces}, Problemi Attuali dell' Analisi e della
Fisica Matematica,
    Gaetano Fichera memorial volume, Aracne, Rome, 2000, 161-166.

\item Maz'ya V., Shaposhnikova, T., {\it Maximal algebra of
multipliers
between fractional Sobolev spaces}, Proceedings of Analysis and
Geometry, Sobolev Institute
Press, Novosibirsk, 2000, pp. 387-400.

\item Maz'ya V., Shaposhnikova, T., {\it Maximal Banach algebra in
spaces
of multipliers between Bessel potential spaces}, Problems and Methods
in
Mathematical Physics, The Siegfried Pr\"ossdorf Memorial Volume, J.
Elschner, I. Gohberg,
B. Silbermann (Eds.), Operator Theory: Advances and Applications, Vol.
121,
Birkh\"auser, Basel, 2001, pp. 352-365.

\item Maz'ya V., Shaposhnikova, T., {\it Sharp pointwise interpolation
inequalities for derivatives},  Journal of Functional
Analysis and its Applications , {\bf 36}:1 (2002), 36-58.

\item Maz'ya V., Shaposhnikova, T., {\it An elementary proof of the
Brezis and
Mironescu theorem on the composition operator in fractional Sobolev
spaces}, The Journal of
Evolution Equations, {\bf 2}, 2002, 113-125 .

\item Maz'ya V., Shaposhnikova, T., {\it On the Bourgain, Brezis, and
Mironescu theorem concerning limiting embeddings of fractional Sobolev
spaces}, The Journal of Functional Analysis, {\bf 195} (2002),
230-238.

\item Maz'ya V., Shaposhnikova, T., {\it On the Brezis and
Mironescu conjecture concerning a Gagliardo-Nirenberg inequality for
fractional Sobolev norms},  Journal des
Math\'ematiques Pures et Appliqu\'es, {\bf 81} (2002), 877-884.

\item Maz'ya V., Shaposhnikova, T., {\it A survey of pointwise 
interpolation inequalities for integer and fractional derivatives}, 
 Acoustics, Mechanics, and Related Topics of Mathematical Analysis, 
A. Wirgin (Ed.), World Scientific, 2002, 212-221.

\item Maz'ya V., Shaposhnikova, T., {\it Erratum to: "On the Bourgain,
Brezis, and Mironescu theorem concerning limiting embeddings of
fractional Sobolev spaces''}, The Journal of Functional Analysis, {\bf
201}:1 (2003), 298-300.


\item Maz'ya V., Shaposhnikova, T., {\it Characterization of
multipliers
in pairs of Besov spaces}, Operator Theoretical Methods and
Applications
to Mathematical Physics: The Erhard Meister Memorial Volume, I.Gohberg et al (Eds.), Birkh\"auser, 2004, 365-387.

\item Maz'ya V., Shaposhnikova, T., {\it Traces of multipliers in
pairs
of weighted Sobolev spaces},  Journal of Function Spaces
and Applications, {\bf 3} (2005), 91-115.

\item Maz'ya V., Shaposhnikova, T., {\it Higher regularity in the layer potential theory}, Indiana Univ.
Math. J. {\bf 54}:1 (2005), 99-142. 

\item Shaposhnikova, T., {\it Three high-stakes math exams},  The Mathematical Intelligencer, {\bf 27}:3 (2005), 44-46.

\item Maz'ya V., Shaposhnikova, T., {\it  A Collection of sharp dilation invariant integral inequalities
for differentiable functions}, in the book: Sobolev Spaces in Mathematics I. Sobolev Type Inequalities, pp. 223--248, 2008, Springer.

\item Shaposhnikova, T., 
{\it Description of pointwise multipliers in pairs of Besov spaces $B_1^k({\bf R}^n)$}, 
  J. for Analysis and its Applications, {\bf 28} (2009), 67-85.

 \item Maz'ya, V., Mitrea, M., Shaposhnikova, T., 
 {\it The inhomogeneous Dirichlet problem for the Stokes system in Lipschitz domains with unit normal close to $VMO$}, J.  Functional  Analysis and its Applications, {\bf 43}: 3 (2009), 217-235.


 \item Maz'ya, V., Mitrea, M., Shaposhnikova, T., 
 {\it The  Dirichlet problem in Lipschitz domains with boundary data in Besov spaces for higher order elliptic systems with rough coefficients}, 
{Journal d'Analyse Math\'ematique}, 
{\bf 110} (2010), 
{167-239}.

\item {Maz'ya, V., Shaposhnikova, T.}, 
{\it Recent progress in elliptic equations and systems of arbitrary order with rough coefficients in Lipschitz domains}, {Bulletin of Mathematical Sciences}, {\bf 1} (2011), 33-77. 

\item{Mazya, V., Shaposhnikova,T.}, 
{\it Brezis-Gallouet-Wainger type inequality for irregular domains}, 
  {Complex Variables and Elliptic Equations}, 
 {\bf 56}: {10} (2011),  {991--1002}. 

\item {Maz'ya, V., Shaposhnikova, T., Tampieri, D.}, 
{\it Solomon Grigoryevich Mikhlin}, 
 {MacTutor, March 2011}, {1--5}.

\item{Shaposhnikova,T.}, 
{\it Inequality for entire functions involving their maximum modulus and maximum terms}, Rend. Lincei, Mat. Appl. {\bf 23}:3 (2012),   259--265.


\end{enumerate}




\subsection*{Translation of books from Russian to English}


\begin{enumerate}
\item Zabreyko P.P., Koshelev A.I., Krasnosel'skii M.A., Mikhlin
S.G., Rakovsh- chik L.S., Stet'senko V.Ya. {\it Integral
Equations -- A Reference Text}, Noordhoff International Publishing,
Leyden, 1975.

\item Mikhlin S.G., {\it Approximation on a Rectangular Grid},
Sijthov and Noordhoff, 1979.

\item Maz'ya V.G., {\it Sobolev Spaces}, Springer-Verlag, 1985.


\item Kresin, G.; Maz'ya, V., {\it  Maximum Principles and Sharp Constants for Solutions of Elliptic and Parabolic Systems},  Mathematical Surveys and Monographs, 183. American Mathematical Society, Providence, RI, 2012. viii+317 pp.
\end{enumerate}

\subsection*{Translation of books by C.S. Lewis from English to
Russian}

\centerline{(Translated for Samizdat in the 70s)}

\begin{enumerate}
\item {\it The Voyage of the Dawn Treader}, Moscow, Variant, 1992;
second edition: Moscow, Sovetskii Compositor, 1992;
Complete Works of C.S. Lewis, vol. 5, Biblia dlya vseh, 2000.

\item {\it The Silver Chair}, Moscow, Variant, 1992; second edition:
Moscow, Sovetskii Compositor, 1992;
Complete Works of C.S. Lewis, vol. 6, Biblia dlya vseh, 2000.

\item {\it The Screwtape Letters}, Moscow, Gnosis-Progress, 1992;
Complete Works of C.S. Lewis, vol. 8, Biblia dlya vseh, 2000; ACT Publishers, Moscow 2004.

\item {\it The Chronicles of Narnia}, Moscow, Ecsmo, 2002,  2005, and 2010. 
\end{enumerate}

\subsection*{Translation  from Swedish to Russian}

\begin{enumerate}
\item {\it Mathematics, Life and Death}, a play by L. G{\aa}rding,
Algebra and Analyses,  Part 1: {\bf 12}:5 (2000), 215-224; Part 2:
{\bf 13}:3
(2001), 229-239; {\it Von Neumann with the Devil}, Algebra and Analyses, {\bf 21}:3 (2009), 1-5.

\item {\it Mechanical Santa Claus (Tomtemaskinen)}, a novel by Sven Nordqvist, OM Publishers, Moscow, 2008.


\item {\it Kerstin and I}, a novel by Astrid Lindgren, Astrel Publishers, Moscow, 2008; Planeta Detstva, Moscow, 2010.

\item  {\it Loranga, Masarin and Dartanjang} a novel by Barbro Lindgren, Samokat Publishers, Moscow, 2009.

\item {\it A book for great fisherman to be}, a novel by Sven Nordqvist and Casper Verner-Carlsson, Ripol Classic Publishers, Moscow, 2011.
%\item   {\it Loranga, Loranga}, a novel by Barbro Lindgren, Samokat Publishers, Moscow, 2010 (to appear).
\end{enumerate}

\subsection*{Translation  from French to Russian}
\begin{enumerate}
\item {\it Huis clos} ({\it Behind closed door}), a play by Jean-Paul Sartr, Blubr.com Publishers, 2010.
\end{enumerate}





\end{document}
